Perception of Work Demands and Resources: <br />Does Sheer Volume Matter?

### 2023-02-18 SIOP2023/Counts/counts_poster.Rmd
Updates to poster

---
title: 'Perception of Work Demands and Resources: Does Sheer Volume Matter?'
author:
  - name: Alicia Stachowski
    affil: 1
  - name: John Kulas
    affil: 2
affiliation:
  - num: 1
    address: University of Wisconsin - Stout
  - num: 2
    address: eRg
column_numbers: 3
primary_colour: "#313ab3"
secondary_colour: "#B4B5B4"
accent_colour: "#FF0000"
logoright_name: 'Stoutlogo_2023.png'
logoleft_name: "erg.png"
output: 
  posterdown::posterdown_html:
    self_contained: false
csl               : "apa7.csl"
bibliography: jobdemands_resources_bibtex.bib
suppress-bibliography: true 
link-citations: true
floatsintext: yes
affiliation_textsize: "50pt"
body_textsize: "48px"
title_textsize:	"75pt"	
author_textsize:	"50pt"
font_family: 'Helvetica'
main_fontfamily: "Helvetica"
#logoleft_name	"Figures/posterdownlogo.png"	Location of the image to use.
#logoright_name	"Figures/posterdownlogo.png"	Location of the image to use.
---

@@

<style>
.logo_left {
 width: 15%;
}
.logo_right {
 width: 15%;
}
.poster_title{
  padding-top: 5%;
  width: 70%;
}
</style>

@@

Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes [e.g., @cavanaugh2000empirical]. Thus:

> *Hypothesis 1a-1c*: A greater overall quantity of resources is positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c)

> *Hypothesis 2a-2c*: A greater overall quantity of challenge demands is positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).

> *Hypothesis 3a-3c*: A greater overall quantity of hindrance demands is negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).

@@

data22$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
data22$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
data22$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)

data22$item387 <- 7-data22$item387
data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
data22$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some

@@

data$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
data$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
data$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)

data$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
data$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
data$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some

@@

eng <- lm(engagement ~ hindrance + challenge + resource, data22)
bur <- lm(burnout ~ hindrance + challenge + resource, data22)
str <- lm(stress ~ hindrance + challenge + resource, data22)

@@

## Limitations & Future Directions 
Future study could consider additional or other O\*Net items, *kinds* of resources or challenges, additional outcomes (e.g., job satisfaction), or whether volume of resources and demands operationalized in this way are related to other behaviors. Finally, there was a moderate relationship between challenges and hindrances, which may be driven by job complexity. With more job elements comes increased opportunities for those elements to be perceived as resources, challenges, or hindrances.

>>>>

---
title: 'Perception of Work Demands and Resources: <br />Does Sheer Volume Matter?'
author:
  - name: Alicia Stachowski
    affil: 1
  - name: John Kulas
    affil: 2
affiliation:
  - num: 1
    address: University of Wisconsin - Stout
  - num: 2
    address: eRg
column_numbers: 3
primary_colour: "#313ab3"
secondary_colour: "#B4B5B4"
accent_colour: "#FF0000"
logoright_name: 'Stoutlogo_2023.png'
logoleft_name: "erg.png"
output: 
  posterdown::posterdown_html:
    self_contained: false
csl               : "apa7.csl"
bibliography: jobdemands_resources_bibtex.bib
suppress-bibliography: true 
link-citations: true
floatsintext: yes
affiliation_textsize: "50pt"
body_textsize: "48px"
title_textsize:	"75pt"	
author_textsize:	"50pt"
font_family: 'Helvetica'
main_fontfamily: "Helvetica"
#logoleft_name	"Figures/posterdownlogo.png"	Location of the image to use.
#logoright_name	"Figures/posterdownlogo.png"	Location of the image to use.
---

@@

<style>
.logo_left {
 padding-top: 0%;
 width: 15%;
}
.logo_right {
 padding-top: 0%;
 width: 15%;
}
.poster_title{
  padding-top: 5%;
  width: 70%;
}
</style>

@@

> *Hypothesis 1a-1c*: Quantity of resources is positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c)

> *Hypothesis 2a-2c*: Quantity of challenge demands is positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).

> *Hypothesis 3a-3c*: Quantity of hindrance demands is negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).

@@

data22$Resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
data22$Hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
data22$Challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)

data22$item387 <- 7-data22$item387
data22$Burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
data22$Stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
data22$Engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some

@@

data$Resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
data$Hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
data$Challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)

data$Burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
data$Stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
data$Engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some

@@

eng <- lm(Engagement ~ Hindrance + Challenge + Resource, data22)
bur <- lm(Burnout ~ Hindrance + Challenge + Resource, data22)
str <- lm(Stress ~ Hindrance + Challenge + Resource, data22)

@@

**Limitations & Future Directions.** 
Future studies could consider additional or other O\*Net items, *kinds* of resources or challenges, additional outcomes (e.g., job satisfaction), or whether volume of resources and demands operationalized in this way are related to other behaviors. Finally, there was a moderate relationship between challenges and hindrances, which may be driven by job complexity - with more job elements comes increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
